Experience Report: Haskell in Computational Biology

### 2012-03-11 mrfy_experience_report.tex
now those damn font warnings are dead!

\authorinfo{Noah M. Daniels \and Andrew Gallant \and Norman Ramsey}
           {Department of Computer Science, Tufts University}
           {\char`\{ndaniels, agallant, nr\char`\}@cs.tufts.edu}

>>>>

\authorinfo{Noah M. Daniels \and Andrew Gallant \and Norman Ramsey}
           {Department of Computer Science, Tufts University}
           {{\rmfamily\{}ndaniels, agallant, nr{\rmfamily\}}@cs.tufts.edu}
